### 2022-03-15 paper2.tex
haven't commited in a while.
Finish paper 2 revisions

\hypertarget{paper-2}{%
\chapter{Information-Seeking Behaviors for Information on Covid-19 Vaccinations}\label{paper-2}}

@@

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory I investigate the factors associated
with each vehicle type when on information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the Covid-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the vehicles queried
in this survey are conceptually different and that the utilization of different
vehicles varies by demography and information sources. Finally, I find that
different fountains of information and information search vehicles hold real
world consequences through their associations with Covid-19 vaccination rates
and intentions, as information from a doctor increased the Covid-19 vaccination
uptake while receiving information from a Social Networking Site like Facebook
or Twitter was associated with lower odds of vaccination.

\textbf{Keywords}: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought of as
harmless \citep{douglas21} some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and the social world that
surrounds them. For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17\% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five \citep{givetash19}. However, even in the ever-evolving
research agenda of misinformation and infodemiology \citep{eysenbach02}, much of the
research focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter with conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.
% cite something else here

The lack of research in which vehicles are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on
“the receiver as an active information seeker and processor." \citep{johnsonComprehensiveModelCancerRelated1993},
though there are always exceptions \citep{eysenbach09}

I use the case of information around Covid-19 vaccinations to explore the
variation of usage of information search vehicles. In doing so, I seek to answer
how computer-mediated or interpersonal information-seeking strategies vary
across populations in their search for information about Covid-19 vaccinations
and investigate how these strategies affect vaccination uptake.

Before addressing my central research questions, I offer an overview of the
current state of social science literature in regards to information-seeking
strategies before providing a description of the research methodology and
analytic sample. I discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

@@

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar
of library and information science, theorized that there are 5 strategies for
searching for information. The most common strategy is browsing, where people
follow leads based on associations without premeditation. Another strategy is
analytical, which includes an explicit consideration of all facets of the
question to guide a search. The empirical method guides the search based on
tactics that were successful in past research. The known site strategy is to go
to the direct source of the information if known. And finally, the similarity
method is to find information based on another similar question that already has
an answer. These 5 strategies vary in their demands for prior knowledge,
cognitive processing, memory, and time spent. While this theory is aimed at
finding information in a library setting, scholars have extended the theory to
other fields and validated the framework
\citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning point
for my theories of information search through network activation or through
computer-mediated communication.

@@

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational, and
instrumental assistance functions performed between social ties and have strong
and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” \citep{winemiller_etal93}[p. 640].
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” \citet{brashersInformationSeekingAvoiding2002}[p. 260].These definitions
help to differentiate between seeking information through social ties or through
something anonymous like online search; a need for coping or deeper
understanding of important matters is thought to sway that decision.

Social support has long been theorized to stem from core discussion networks and
much of the historical social support surveys only looked at these core
networks. The underlying assumption is that individuals reach out to a handful
of strong ties when in need of support, which could be elicited in surveys using
name generators \citep{marsdenCoreDiscussionNetworks1987}. This approach has yielded
important insights, but largely overlooks crucial
processes of resource activation \citep{hurlbertCoreNetworksTie2000,
perrySocialNetworkActivation2015, smithDonPutMy2005}. For instance, Small
\citet{smallSomeoneTalk2017} shows that the core discussion network does not capture
how people activate social support in practice and indicates that people draw on
much broader social connections for support, reminiscent of the weak ties
research by Granovetter \citet{granovetterStrengthWeakTies1973}. There is ongoing
research investigating how weak-tie support holds for different support types
based on the architecture put forward by 
\citet{houseStructuresProcessesSocial1988} of instrumental, emotional, and
informational support.

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. While Small
\citet{smallSomeoneTalk2017} focuses on how support can depend on a network tie
simply "happened to be there", online search is theoretically the most
frictionless and costless mode of support. No social capital or relationship is
necessary when choosing to utilize a search engine.

There are three computer-mediated vehicles I consider for this analysis: online
search engines like Google or Bing, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
or Twitter. While the first two are largely anonymous and don't require a
personal network, the third is a unique hybrid between personal network
connections and online search.

There are important factors that can influence information-seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s  \citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. \citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

@@

@@

The data used for this research project are based on original survey data
sampled between December 03, 2021 through
December 12, 2021. This survey was hosted on Qualtrics and
participants were paid and recruited using Amazon Turk (MTurk). The total valid
survey responses (\emph{n} = 948) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g., social network alters
consistently named random nouns), or taking the survey more than once. The same
is slighted gender unbalanced, slightly skewing towards a male sample. For the
respondents who provided their zip code (p = 0.98), the sample is quite balanced with a slight skew towards MTurkers in the South (p = 0.41).

The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes. The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes. Participants were paid \$6.00 for their time after Amazon administrative fees, funded by a Grant awarded to Kelsey E. Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
Science and the Russell Sage Foundation. The main portion of this survey replicates the book, Someone to Talk To \citep{smallSomeoneTalk2017} by expanding on Small's finding that people draw on much broader sources than ``important people'' for support by segregating weak-tie social support into instrumental, emotional, and informational support \citep[see][]{houseStructuresProcessesSocial1988}. The latter
part of the survey focuses on resource activation for the specific case-study of
information during the Covid-19 pandemic analyzed in this paper.

\input{tables/paper2/table-1-desc}

@@

There are multiple dependent variables of interest for this paper. The first
variable is a dichotomous indicator of whether someone intentionally sought out
information about Covid-19 vaccinations. The survey asked, ``And how about you
yourself intentionally looking for information about a Covid-19 vaccine? Such
information can include things such as advice, clarification, facts, and
experiences.'' About 78\% (\(\widehat{p}\))
of respondents had intentionally sought out information about Covid-19
vaccinations (95\% Confidence Interval = \{76\%, 81\%\}).

Further dependent variables segment the above question into multiple options;
``How did you look for information about the Covid-19 vaccine?'' Respondents were
posed with 5 responses and `other,' of which they could select multiple. The
largest proportion, 44\%, asked their `doctor or another health professional' (95\% Confidence Interval = \{41\%, 47\%\}). About 42\% said they asked, `a person
like friend, neighbor, or family member that {[}they{]} know' (95\% Confidence
Interval = \{39\%, 45\%\}). An additional 41\% searched `for {[}their{]} question
using an online search engine such as Google or Bing' (95\% Confidence Interval
= \{38\%, 45\%\}). About a quarter of the sample, 27\%, `posted queries in an
online discussion group, listserve, or other online forum like a Facebook Group
or Subreddit' (95\% Confidence Interval = \{24\%, 30\%\}). And finally, 18\% of the sample `posted queries on a social networking site such as Facebook timeline, Twitter status update, or LinkedIn' (95\% Confidence Interval = \{16\%, 21\%\}).
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 \citep{scanlon19}.

\input{tables/paper2/table-2-desc}

@@

Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination against Covid-19. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About 87\% have a
positive view about the vaccine. This construct is made through the combination
of two survey items. The first item is actual vaccination status, obtained through
the question `Did you receive a Covid-19 vaccine?'
84\% of the sample said that
they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the national vaccination rate is closer to 75\% \citep{cdc20}, this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to `Vaccination Outlook' was only given to those who had not
responded `yes' to the to their vaccination status. These respondents were asked `Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?' Of those
who were asked this question (n = 147), 9\% said they were `definitely yes' getting the vaccine;
9\% said they were `probably yes' going to receive vaccine. The rest of the sample was more unsure: 15\% said they `Might or might not,' 26\% said `Probably not,' and finally 41\% said they would `definitely not' receive the vaccine. The variable `Vaccination Outlook' indicates that either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

@@

The first independent variables used in this analysis are based on the question,
`In the past 12 months, without searching for it, did you receive information
about the Covid-19 vaccine from \ldots{} (check all sources you received information
from).' This differs from the `How did you look for information' question above
because this is based on passive reception of information. The largest proportion
of respondents had received information from a person like friend, neighbor, or
family member that {[}they{]} know (\(\widehat{p}\) = 67\%
). Respondents also commonly received information from a television news channel
or a newspaper, about 65\% of the sample.
47\% of the sample had received information from
their doctor or other health professional while 40\%
received information from a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserve, or other
online forum like a Facebook group or subreddit
(\(\widehat{p}\) = 35\%).

We also asked various demographic questions to understand our sample. The
average age of our sample was 37.76. Our sample was 44\% female, and 55\% male. The sample is diverse racially though some ethnic groups are underrepresented compared to national averages. Race was evaluated using the
question, `What is your race? If you are ``mixed race,'' select all that apply.'
Because of the multi-selection question, each variable is dichotomous and
proportions are shown. 88\% of the sample claimed
they were `White,' 8\% claimed to be `Black or
African American,' 3\% chose `American Indian or
Alaskan Native,' 4\% selected `Asian,' and finally
when asked, `Are you Hispanic, Latino/a/x, or Latin American Origin?'
15\% selected `Yes.' Respondents were also asked to
select the highest level of education that you have completed. Based on the
breakdown between `Less than high school,' `High school graduate,' `Some college,'
`Associate's or Technical degree,' `Bachelor's degree,' and `Graduate or
professional degree,' 74\% of the sample were classified
to have a college-level education (Associate's degree or above).

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-desc}
\& \ref{tab:table-2-desc}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of Binomial Generalized Linear Models \citep{venables2002a}. In Table \ref{tab:table-model-1}\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} \citep{modelsummary}}
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information seeking.\footnote{Figures in this paper were all created using the \texttt{r} packages jtools \citep{jtools} and ggplot2 \citep{wickham_etal, wickham11}}.
In Table \ref{tab:model-2-phi} I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about Covid-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient \citep{warrens08}, otherwise
known as a mean square contingency coefficient which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
associations between my predictors and the 5 information search vehicles by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\hypertarget{information-seeking}{%
\subsection{Information Seeking}\label{information-seeking}}

@@

\begin{figure}[h]
{\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
\caption{What predicts someone intentionally searched for information, Plot of Coefficients}\label{fig:plot-model-1}
\end{figure}

>>>>

\hypertarget{paper-2}{%
\chapter{Information-Seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}

@@

Previous research has greatly failed to distinguish between the activation of
information-seeking behaviors online and offline. Using theories of 1) social
support and 2) uses and gratifications theory I investigate the factors associated
with each vehicle type when on information-seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the COVID-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the vehicles queried
in this survey are conceptually different and that the utilization of different
vehicles varies by demography and information sources. Finally, I find that
different sources of information exposure and information search vehicles hold real
world consequences through their associations with COVID-19 vaccination rates
and intentions, as information from a doctor increased the COVID-19 vaccination
uptake while receiving information from a Social Networking Site like Facebook
or Twitter was associated with lower odds of vaccination.

\textbf{Keywords}: Information-Seeking Behavior, COVID-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought of as
harmless \citep{douglas21} some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and public health.
For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17\% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five \citep{givetash19}. However, even in the ever-evolving
research agenda of misinformation and infodemiology \citep{eysenbach02}, much of the
research focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter with conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.
% TODO cite something else here

The lack of research in which vehicles are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on “the receiver as an active information seeker and processor." 
\citep{johnsonComprehensiveModelCancerRelated1993}
\citep[for an exception, see]{eysenbach09}.

I use the case of information around COVID-19 vaccinations to explore the
variation of usage of information search vehicles. In doing so, I seek to answer
how computer-mediated or interpersonal information-seeking strategies vary
across populations in their search for information about COVID-19 vaccinations
and investigate how these strategies affect vaccination uptake. Specifically, this article 
answers two research questions: (1) How do computer-mediated or interpersonal information-seeking
strategies vary across populations? (2) How does the information search vehicle utilized 
affect COVID-19 Vaccination uptake?

Before addressing the results to these research questions, I offer an overview of the
current state of social science literature in regards to information-seeking
strategies and providing a description of the research methodology and
analytic sample. I then discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

@@

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar
of library and information science, theorized that there are five strategies for
searching for information: browsing, analytical, empirical, known site, and similarity. 
The most common strategy is browsing, where people
follow leads based on associations without premeditation. Another strategy is
analytical, which includes an explicit consideration of all facets of the
question to guide a search. The empirical method guides the search based on
tactics that were successful in past research. The known site strategy is to go
to the direct source of the information if known. And finally, the similarity
method is to find information based on another similar question that already has
an answer. These five strategies vary in their demands for prior knowledge,
cognitive processing, memory, and time spent. While this theory is aimed at
finding information in a library setting, scholars have extended the theory to
other fields and validated the framework
\citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning point
for my theories of information search through network activation or through
computer-mediated communication.

@@

One way to find information is to activate network ties to secure information
through a form of social support. Social support, while previously used
interchangeably with the terms social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational, and
instrumental assistance functions performed between social ties and have strong
and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” \citep[][p. 640]{winemiller_etal93}.
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” \citet[][p. 260]{brashersInformationSeekingAvoiding2002}.These definitions
help to differentiate between seeking information through social ties or through
something anonymous like online search; a need for coping or deeper
understanding of important matters is thought to sway that decision.

Social support has long been theorized to stem from core discussion networks and
much of the historical social support surveys only examined these core
networks. The underlying assumption is that individuals reach out to a handful
of strong ties when in need of support, which could be elicited in surveys using
name generators \citep{marsdenCoreDiscussionNetworks1987}. This approach has yielded
important insights, but largely overlooks crucial
processes of resource activation \citep{hurlbertCoreNetworksTie2000,
perrySocialNetworkActivation2015, smithDonPutMy2005}. For instance, Small
\citet{smallSomeoneTalk2017} shows that the core discussion network does not capture
how people activate social support in practice and indicates that people draw on
much broader social connections for support, reminiscent of the weak ties
research by Granovetter \citet{granovetterStrengthWeakTies1973}. There is ongoing
research investigating how weak-tie support holds for different support types
based on the architecture put forward by 
\citet{houseStructuresProcessesSocial1988} of instrumental, emotional, and
informational support.

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”, or the utilization of internet search engines. 
As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. Small
\citet{smallSomeoneTalk2017} showed that Graduate students often
confided in a "miscellaneous classmates encountered down the hall" (p.
176) instead of established and trusted confidants because they
simply were there at the right time. I theorize that online search engines
may be the most frictionless and costless mode of support. 
No social capital or relationship is necessary when choosing to utilize a search engine.

There are three computer-mediated vehicles I consider for this analysis: online
search engines like Google or Bing, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
or Twitter. While the first two are largely anonymous and do not require a
personal network, the third is a unique hybrid between personal network
connections and online search.

There are important factors that can influence information-seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. 
UGT posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s  
\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. 
\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. 
\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

\begin{hyp}[H\ref{hyp:online-vs-network}] \label{hyp:online-vs-network}
The proportion of survey respondents who seek information
using an online search engine will be significantly higher than those who
need to activate network resources, like asking a friend.
\end{hyp}

@@

\begin{hyp}[H\ref{hyp:drgooglefriend}] \label{hyp:drgooglefriend}
Seeking information from experts, search engines, and other people
will be the most common modes of information search. 
\end{hyp}

@@

The data used for this research project are based on original survey data
collected between December 03, 2021 through December 12, 2021.
This survey was hosted on Qualtrics and participants were paid and 
recruited using Amazon Turk (MTurk). Potential MTurkers were invited
to participate if they were located in the United States, had a task
rate approval of over 95 percent, had completed 50 tasks, and had not 
completed this survey in previous sessions. The total valid 
survey responses (\emph{n} = 948) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g., social network alters
consistently named random nouns), or taking the survey more than once. The sample
is slightly gender unbalanced, skewing towards male respondents. For the
respondents who provided their zip code (p = 0.98), the sample is quite balanced with
a slight skew towards MTurkers in the South (p = 0.41).

The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes.
The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes.
Participants received \$6.00 in compensation for their participation in the survey
\footnote{All funding for this survey was provided by a Grant awarded to Kelsey E. 
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social Science
and the Russell Sage Foundation.}. The survey consisted of two main parts. The
first portion of the survey is a replication of they survey conducted by 
\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on 
support activation by segregating weak-tie social support into instrumental, 
emotional, and informational categories \citep[see][]{houseStructuresProcessesSocial1988}.
The second part of the survey focuses on network resource activation and 
information-seeking behaviors of individuals regarding COVID-19 vaccinations
for this paper.

\input{tables/paper2/table-1-ind}

@@

There are multiple dependent variables of interest for this paper. The first
variable is a dichotomous indicator of whether someone intentionally sought out
information about COVID-19 vaccinations. The survey asked, ``And how about you
yourself intentionally looking for information about a COVID-19 vaccine? Such
information can include things such as advice, clarification, facts, and
experiences.'' About 78\% (\(\widehat{p}\))
of respondents had intentionally sought out information about COVID-19
vaccinations (95\% Confidence Interval = \{76\%, 81\%\}).

Further dependent variables segment the above question into multiple options;
``How did you look for information about the COVID-19 vaccine?'' Respondents were
posed with 5 responses and `other,' of which they could select multiple. The
largest proportion, 44\%, asked their `doctor or another health professional'.
About 42\% said they asked, `a person like friend, neighbor, or family member 
that [they] know'. An additional 41\% searched `for [their] question
using an online search engine such as Google or Bing'. About a quarter of the
sample, 27\%, `posted queries in an online discussion group, listserv, or 
other online forum like a Facebook Group or Subreddit'. And finally, 18\% of 
the sample `posted queries on a social networking site such as Facebook timeline, 
Twitter status update, or LinkedIn'.
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 \citep{scanlon19}.

@@

\input{tables/paper2/table-2-dep}

Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination against
COVID-19. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About 87\% have a
positive view about the vaccine. This construct is made through the combination
of two survey items. The first item is actual vaccination status, obtained through
the question `Did you receive a COVID-19 vaccine?'
84\% of the sample said that
they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}).
As the national vaccination rate is closer to 75\% \citep{cdc20}, this indicates 
some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to `Vaccination Outlook' was only given to those who had not
responded `yes' to the to their vaccination status. These respondents were asked 
`Do you plan to receive a vaccine for the prevention of the COVID-19 virus?' Of those
who were asked this question (n = 147), 9\% said they were `definitely yes' getting the vaccine;
9\% said they were `probably yes' going to receive vaccine. The rest of the sample was
more unsure: 15\% said they `Might or might not,' 26\% said `Probably not,' and finally
41\% said they would `definitely not' receive the vaccine. The variable `Vaccination 
Outlook' indicates that either the respondent received a COVID-19 vaccine or
either probably or definitely will in the future.

@@

The first independent variables used in this analysis are based on the question,
`In the past 12 months, without searching for it, did you receive information
about the COVID-19 vaccine from \ldots{} (check all sources you received information
from).' This differs from the `How did you look for information' question above
because this is based on passive reception of information. The largest proportion
of respondents had received information from "a person like friend, neighbor, or
family member that [they] know" (\(\widehat{p}\) = 67\%). Respondents
also commonly received information from a television news channel
or a newspaper, about 65\% of the sample.
47\% of the sample had received information from
their doctor or other health professional, while 40\%
received information from a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserv, or other
online forum like a Facebook group or subreddit
(\(\widehat{p}\) = 35\%).

We also asked various demographic questions to describe our sample. The
average age of our sample was 37.76. 44\% of our sample self-identified as female, 
while 55\% self-identified as male. The sample is diverse racially though some ethnic
groups are underrepresented compared to national averages. Race was evaluated using the
question, `What is your race? If you are ``mixed race,'' select all that apply.'
Because of the multi-selection question, each variable is dichotomous and
proportions are shown. 88\% of the sample claimed
they were `White,' 8\% claimed to be `Black or
African American,' 3\% chose `American Indian or
Alaskan Native,' 4\% selected `Asian,' and finally
when asked, `Are you Hispanic, Latino/a/x, or Latin American Origin?'
15\% selected `Yes.' Respondents were also asked to
select the highest level of education that you have completed. Based on the
breakdown between `Less than high school,' `High school graduate,' `Some college,'
`Associate's or Technical degree,' `Bachelor's degree,' and `Graduate or
professional degree,' 74\% of the sample were classified
to have a college-level education (Associate's degree or above).

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind}
\& \ref{tab:table-2-dep}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of binomial generalized linear models with a logit link \citep{venables2002a},
otherwise known as logistic regression model \citep{hothorn2006handbook}.
This approach is appropriate because the data
are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} 
\citep{modelsummary}},I fit a logistic regression model predicting
whether someone sought information about COVID-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information-seeking.\footnote{Figures 
in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
and ggplot2 \citep{wickham_etal, wickham11}}.
In Table \ref{tab:model-2-phi}, I disaggregate information-seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about COVID-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient \citep{warrens08}, otherwise
known as a mean square contingency coefficient, which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
associations between my predictors and the five information search vehicles by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information exposure sources, information-seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\hypertarget{information-seeking}{%
\subsection{information-seeking}\label{information-seeking}}

@@

\begin{figure}[h]
{\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
\caption{What predicts someone intentionally searched for information, Plot of Coefficients?}\label{fig:plot-model-1}
\end{figure}

Table \ref{tab:table-model-1} provides the results of my logistic regression
analysis predicting whether someone sought information about COVID-19. These
initial results suggest similar results for each vehicle of information
delivery: each mode of receiving information whether from a doctor, a person,
the news, a social networking site, or an online forum, all increase the odds of
seeking out information. For example, respondents who had received information
from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta k)\),
\emph{p} \textless{} 0.001) times more likely to seek out information over someone
who had not. Similarly, respondents who had received information from `a
person like friend, neighbor, or family member that [they] know' were 1.87
(\emph{p} \textless{} 0.001) times more likely to seek out information over 
someone who had not received information from a person like that. Interesting, 
those who had received information from an online discussion group, listserv,
or other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
\textless{} 0.001) times more likely to search out more information than 
someone who had not. While most demographic variables do not seem to have a 
strong effect on whether someone sought out information about the COVID-19 
vaccine, a few key variables had strong associations.  Respondents who are 
older are more likely to seek information; The odds are about 3\% higher when 
age is equal to x + 1 relative to x, possibly indicating a generational effect
of information-seeking patterns (\emph{p} \textless{} 0.01). Additionally,
those who were more educated, that is those with an Associate's degree or higher,
were 1.58 more likely to seek additional information than those without the degree
(\emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
African American sample was more likely to seek out information, specifically:
Blacks were 3.58 times more likely to seek out information over non-Blacks (\emph{p}
\textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
between the coefficients and information-seeking.
